---
date: "`r format(Sys.time(), '%d %B, %Y')`"
params:
   rmd: "prepareReport.Rmd"
output:
  html_document:
  highlight: tango
  number_sections: no
  theme: default
  toc: yes
  toc_depth: 3
  toc_float:
    collapsed: no
    smooth_scroll: yes
---
```{r, echo=FALSE}
library(data.table)
library(dplyr)
load(snakemake@input[[6]])

before_genes <- nrow(metadata_$raw_dataset)
before_samples <- ncol(metadata_$raw_dataset)
after_genes <- nrow(metadata_$filtered_dataset)
after_samples <- ncol(metadata_$filtered_dataset)

topMadPng <- file.path(snakemake@config[["out_dir"]], 'resources', 'preprocess', 'topMAD.png')
madMedPng <- file.path(snakemake@config[["out_dir"]], 'resources', 'preprocess', 'mad-med.png')
svdBeforePng <- file.path(snakemake@config[["out_dir"]], 'resources', 'preprocess', 'svdBefore.png')
distancesBeforePng <- file.path(snakemake@config[["out_dir"]], 'resources', 'preprocess', 'distancesBefore.png')
svdAfterPng <- file.path(snakemake@config[["out_dir"]], 'resources', 'preprocess', 'svdAfter.png')
distancesAfterPng <- file.path(snakemake@config[["out_dir"]], 'resources', 'preprocess', 'distancesAfter.png')
distancesToZeroBeforePng <- file.path(snakemake@config[["out_dir"]], 'resources', 'preprocess', 'distances_to_zero_before.png')
distancesToZeroAfterPng <- file.path(snakemake@config[["out_dir"]], 'resources', 'preprocess', 'distances_to_zero_after.png')
```

---
pagetitle: "`r snakemake@config[['cell_types']]`CT `r snakemake@config[['analysis_name']]`"
---

## Dataset: `r snakemake@config[['dataset']]`
## Cell types: `r snakemake@config[['cell_types']]`
## Run Id: `r snakemake@params[['run_id']]`

## Parameters
analysis_name: `r snakemake@config[['analysis_name']]`<br>
num_inits: `r snakemake@config[['num_inits']]`<br>
top_mad: `r snakemake@config[['top_mad']]`<br>
min_mad: `r snakemake@config[['min_mad']]`<br>
min_median: `r snakemake@config[['min_median']]`<br>
filter_genes: `r snakemake@config[['filter_genes']]`<br>
filter_samples: `r snakemake@config[['filter_samples']]`<br>
scale_iterations: `r snakemake@config[['scale_iterations']]`<br>
init_strategy: `r snakemake@config[['init_strategy']]`<br>

### Blocks
```{r, echo=FALSE}
knitr::kable(as.data.frame(fread(snakemake@config[['blocks_pipeline']])))
```

## Preprocessing
Number of genes (before filtering, only with MAD>0): `r before_genes`<br>
Number of samples (before filtering): `r before_samples`<br>

<h3>MAD distribution</h3>
<img src="`r base64enc::dataURI(file = topMadPng, mime = 'image/png', encoding = 'base64')`"></img>
<h3>MAD vs Median expression</h3>
<img src="`r base64enc::dataURI(file = madMedPng, mime = 'image/png', encoding = 'base64')`"></img>
<h3>SVD (before filtering)</h3>
<img src="`r base64enc::dataURI(file = svdBeforePng, mime = 'image/png', encoding = 'base64')`"></img>
<h3>Distances to zero (before filtering)</h3>
<img src="`r base64enc::dataURI(file = distancesToZeroBeforePng, mime = 'image/png', encoding = 'base64')`"></img>
<h3>Distances to zero (after filtering)</h3>
<img src="`r base64enc::dataURI(file = distancesToZeroAfterPng, mime = 'image/png', encoding = 'base64')`"></img>
<h3>Distances (before filtering)</h3>
<img src="`r base64enc::dataURI(file = distancesBeforePng, mime = 'image/png', encoding = 'base64')`"></img>
<h3>SVD (after filtering)</h3>
<img src="`r base64enc::dataURI(file = svdAfterPng, mime = 'image/png', encoding = 'base64')`"></img>
<h3>Distances (after filtering)</h3>
<img src="`r base64enc::dataURI(file = distancesAfterPng, mime = 'image/png', encoding = 'base64')`"></img>

Number of genes (after filtering): `r after_genes`<br>
Number of samples (after filtering): `r after_samples`<br>

## Results
```{r, echo=FALSE}
knitr::kable(as.data.frame(fread(snakemake@input[[1]],sep="\t")))
```
## UMAP
<img src="`r base64enc::dataURI(file = snakemake@input[[9]], mime = 'image/png', encoding = 'base64')`"></img>

## Best initialization
<h3>Trajectory plot</h3>
<img src="`r base64enc::dataURI(file = snakemake@input[[2]], mime = 'image/png', encoding = 'base64')`"></img>
<h3>Number of negative proportions</h3>
<img src="`r base64enc::dataURI(file = snakemake@input[[4]], mime = 'image/png', encoding = 'base64')`"></img>
<h3>Number of negative elements in basis</h3>
<img src="`r base64enc::dataURI(file = snakemake@input[[3]], mime = 'image/png', encoding = 'base64')`"></img>
<h3>Sum-to-one constraint</h3>
<img src="`r base64enc::dataURI(file = snakemake@input[[5]], mime = 'image/png', encoding = 'base64')`"></img>
<h3>Proportions</h3>
<img src="`r base64enc::dataURI(file = snakemake@input[[10]], mime = 'image/png', encoding = 'base64')`"></img>
<h3>Markers</h3>
```{r, echo=FALSE}
  top_genes  <- 20
  cell_types <- metadata_$cell_types
  basis_ <- data.frame(fread(snakemake@input[[8]])) %>%
    dplyr::rename(gene = "V1")
  basis_ <- basis_[-1,]
  genesList <- data.frame(genes=rep(" ",cell_types))
  rownames(genesList) <- paste0("Cell_type_",1:cell_types)
  
  for (ct in 1:cell_types) {
    row_name <- paste0("Cell_type_",ct)
    genes <- (basis_ %>% arrange(desc(.data[[row_name]])))[1:top_genes,"gene"]
    genesList[row_name,"genes"] <- paste0(genes,collapse = " ")
  }
  knitr::kable(genesList)
```

<a href="`r base64enc::dataURI(file = snakemake@input[[7]], mime = 'text', encoding = 'base64')`">Download proportions</a><br>
<a href="`r base64enc::dataURI(file = snakemake@input[[8]], mime = 'text', encoding = 'base64')`">Download basis</a><br>